### 2012-02-11 GUIErrorDetector/paper/evaluation.tex
trivial edit

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
This variant ran out of memory on all subjects, and did not output any real
errors before it terminated.  The number of
non-cyclic paths in a graph is exponential in the graph size, and it 
it is infeasible to enumerate all paths.
for a realistic call graph, which often contains thousands of nodes.
%only a very few amount of paths can be enumerated within a practical amount of time.

>>>>

The third variant uses exhaustive search to find potential errors. This variant
enumerates all non-cyclic paths from all reachable \CodeIn{Thread.start()} nodes
to each UI-accessing node, and then checks whether each
path spawns a new thread and accesses GUI objects without using safe UI methods.
This variant ran out of memory on all subjects, and did not output any real
errors before it terminated.  The number of
non-cyclic paths in a graph is exponential in the graph size, and it 
it is infeasible to enumerate all paths
for a realistic call graph, which often contains thousands of nodes.
%only a very few amount of paths can be enumerated within a practical amount of time.
